---
title: "Predicting NFL Wide Receiver Success Using PFF and NFL Combine Data"
author: "Jack Miller, Namh Lahade, Matthew Paul, Caspian Svenson"
output: pdf
---

```{r load packages, warning = FALSE, message=FALSE}
library(tidyverse)
library(tidyr)
library(readr)
library(dplyr)
library(broom)
library(knitr)
library(nflfastR)
library(nflplotR)
library(ggrepel)
library(caret)
library(pROC)
```

```{r load-data}
readRDS("full_data.rds")
```



# 1 Introduction

## 1.1 Background Information

Scouting is one of the most important aspects of roster construction in the NFL. For many years, traditional scouting methods have involved watching tape and evaluating players using the "eye-test". However, many analytical scouting methods are starting to complement these traditional scouting methods. Two of the biggest analytical 

## 1.2 Aims

The main goal of our project is to test which college statistics, NFL Combine results, and PFF grades are significant to predicting whether a player will make it to the NFL and be successful.

## 1.3 Exploratory Data Analysis




# 2 Methods

## 2.1 Analysis Plan



## 2.2 Modeling

#### College Model

Our first model examines NFL prospects' college statistics and PFF grades in trying to predict whether they will make it to the league.


#### Combine Model

Our second model also examines NFL prospects' college statistics and PFF grades in trying to predict whether they will make it to the league. However, we also include Combine and Pro Day statistics for players who either attended the NFL Combine or have available Pro Day times.

#### NFL Model

Our final model only examines 

## 2.3 Model Diagnostics



## 2.4 Model Selection



# 3 Results

## 3.1 Predicting Who Will Play in the NFL





## 3.2 Predicting Who Will Be Successful in the NFL






# 4 Discussion


# 5 References

