---
title: "Predicting Success of NFL Proespects Using PFF and Combine Results"
subtitle: "2023 DSAC Final Project"
author: "Jack Miller, Namh Lahade, Caspian Svenson, "
format:
  pdf:
    fontsize: 11pt
    geometry:
      - top = 10mm
      - bottom = 25mm
      - left = 22mm
      - right = 22 mm
bibliography: references.bib
nocite: |
  @*
editor: visual
execute:
  echo: false
  results: false
  warning: false
  message: false
editor_options: 
  chunk_output_type: console
---

```{r load packages, warning = FALSE, message=FALSE}
library(tidyverse)
library(tidyr)
library(readr)
library(dplyr)
library(broom)
library(knitr)
library(nflfastR)
library(nflplotR)
library(ggrepel)
library(caret)
library(pROC)
```

```{r load-data}
full_data <- readRDS("full_data.rds")
combine_cleaned <- readRDS("combine_cleaned.rds")
college_data <- readRDS("college_data.rds")
```

# 1 Introduction

## 1.1 Background Information

Scouting is one of the most important aspects of roster construction in the NFL. For many years, traditional scouting methods have involved watching tape and evaluating players using the "eye-test". However, many analytical scouting methods are starting to complement these traditional scouting methods. Two of the biggest analytical.

One of the hardest positions to scout in the NFL is the Wide Receiver (WR). Because teams use varying amounts of receivers and varying types of receivers, there is much that goes into being a good and productive WR in the NFL.

## 1.2 Aims

The main goal of our project is to test which college statistics, NFL Combine results, and PFF grades are significant to predicting whether a player will make it to the NFL and be successful. Previous work to predict NFL success among college draft prospects has focused solely on college statistics and combine numbers. We hope to be one of the first groups to understand the impact that PFF college grades in addition to these scouting metrics have on predicting whether a player will make it to the league and whether they will be successful. Because PFF college grades only became available for Division 1 athletes in 2014 and we also want to use NFL statistics to measure success, we chose to only use NFL draft classes with two years of college data and two years of NFL data. This means we are only examining the 2016-2020 NFL draft classes as these are the only players we have enough professional and college data to examine.

## 1.3 Exploratory Data Analysis




# 2 Methods

## 2.1 Analysis Plan

## 2.2 Modeling

#### College Model

Our first model examines NFL prospects' college statistics and PFF grades in trying to predict whether they will make it to the league.

#### Combine Model

Our second model also examines NFL prospects' college statistics and PFF grades in trying to predict whether they will make it to the league. However, we also include Combine and Pro Day statistics for players who either attended the NFL Combine or have available Pro Day times.

#### NFL Model

Our final model only examines

## 2.3 Model Diagnostics

## 2.4 Model Selection

# 3 Results

## 3.1 Predicting Who Will Play in the NFL

## 3.2 Predicting Who Will Be Successful in the NFL

# 4 Discussion

# 5 References
